\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-01-31 letter.tex
add first part of note on E6 to letter (had forgotten on 1/25)
add paragraph on E4 to letter

@@

>>>>

Editor's point $\#$3: Thank you for the suggestion to add an extensive form and to define the game more clearly and formally. I think the addition of the normal form in Figure 1 made this portion of the paper, in the new subsections 2.1 (The Basic Setup) and 2.2 (Preferences) significantly more readable. I hope you will agree.

@@

Editor's point $\#$6: I have removed the duplicate statement of Assumption 1. [{\color{blue} much more to do here}]
